Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Update Stojanovsky reference
Update todo
Expand on analysis of the collision study

The OSM project is based on Volunteered Geographical Information (VGI).
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents (Haklay 2010).
Particularily the high resolution imagery from Bing in 2010 led to an increase in building information in OSM (Fan et al, 2014).

@@

% TODO: Proper citations (Fix links)
% TODO: Expand on analysis about Feature overlap

@@

The biggest reason is thought to be that footpaths in their nature are narrow, so narrow that they can be displaced by more than half of their full width before the positional accuracy is reached.

Conslusion: footpaths were not worse than other categories, which are included in many unity packages already
(Fan et al, 2014) claimed that the positional error is largely due to the limited resolution in satellite imagery.

3189 features collide and 7330 of edges.
This means that for each colliding road, on average 2.3 of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are 26473 feautures 6382579 edges, meaning that each feature on average is contructed out of 241 edges.
Thus the percentage of edges colliding per road is on average roughly 0.95\%.
A similar calculation for the number of features that could not be corrected by translation yields that the number of colliding edges per feature is on average 1.2, and that the percentage of colliding edges per feature is 0.49\%.
The conclusion is that most often, a small part of a road is colliding, and will need correction.
Visual inspection of the cases where roads collide with other features has supported this.

After visual inspection of the cases where features collide, it was determined that all collision occurences can be almost exclusively classified into one of five categories:

@@

Each case is exemplified in figure \ref{fig:collision-cases}.

@@

All these cases will create issues when generating the 3D mesh representation of the city.

@@

\bibitem{stojanovski-20}
Stojanivski T. 2020. Viewpoint: City Information Modeling (CIM) And Digitizing Urban Design Practises.
Under review

>>>>

The OSM project is based on Volunteered Geographical Information (VGI).
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents (Haklay 2010).
Particularily the high resolution imagery from Bing in 2010 led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery. (Fan et al, 2014).

@@

@@

The immediate conclusion of this study is that, in terms of feature collision, footpaths were not significantly worse than other road categories.
As a result, it can promptly be assumed that city modelling services which already utilize OSM car road data could also use OSM footpath data without a drastic increase in feature collision.
The biggest reason for this is thought to be that footpaths in their nature are narrow.
So narrow in fact that they can be displaced by more than half of their full width (minimum 1 meter) before the limit of half the positional accuracy (1.025 meters) is reached.

Looking closer at the individual collision cases, the next conclusion is that most often it is actually a small part of a road that is colliding, and will need correction.
We make an exemplifying calculation to support this claim.
Looking in tables \ref{table:road-collision} and \ref{table:road-collision-corrected}, we note that before road extrusion, 3189 features and 7330 of their edges are intersecting some other feature.
This means that for each colliding road, on average 2.3 of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are 26473 feautures and 6382579 edges, meaning that each road feature is on average contructed out of 241 edges.
Thus the percentage of edges colliding per road is on average roughly 0.95\%.
A similar calculation for the number of features that could not be corrected by translation yields that the number of colliding edges per feature is on average 1.2, and that the percentage of colliding edges per feature is 0.49\%.
Visual inspection of the cases where roads collide with other features has supported this.

After visual inspection of the cases where features collide, it was determined that all collision occurences can be almost exclusively classified into one of five categories.
These categories are explained in the list below, and each case is exemplified in figure \ref{fig:collision-cases}.
All these cases will create issues when generating the 3D mesh representation of the city.

@@

@@

@@

\bibitem{stojanovski-20}
Stojanivski T. (2020). Viewpoint: City Information Modeling (CIM) And Digitizing Urban Design Practises. Article. Under review.
